\LARGE \bf On the use of vehicle categorization and context information for messages forwarding in VANETs

### 2016-09-16 paperITSC.tex
Introduction commit test

Vehicular Ad hoc NETworks (VANETs) are sub class of Mobile Ad hoc NETworks with unique characteristics like high speed of nodes and dynamic network topology. To disseminate data, VANETs enable communications between mobile nodes and infrastructure network. These networks support a large number of applications such as accident avoidance, intelligent traffic control and data dissemination, thereby, providing safety, comfort and convenience to the users \cite{conprova2013}.

The nodes (vehicles) in VANETs contain hundreds of on-board sensors, which provide useful information about vehicle state (e.g., engine status, vehicle position, speed, heading) and surrounding environment (e.g., road and traffic condition, and weather forecast). Vehicles that collect, disseminate and make use of this contextual information are called context-aware vehicles \cite{grilli2009}. Context-awareness is important for the deployment of a large number of new applications. However, providing reliable and efficient dissemination of contextual information is a challenging task in VANETs. It is important to share only relevant information among vehicles, in order to reduce the communication overhead \cite{kumar2015}.

The importance of vehicles categorization for providing contextual information has been recently addressed in \cite{zhang2012, zhang2014}. We can categorize the vehicles into taxi, bus, private car, and cargo. Each of them has a different mobility pattern. For example, a bus has its own predefined route, timing and schedule. On the other hand, a taxi has no restricted mobility and it can follow different routes in different times, based on passengers demands and drivers preferences. Such mobility information could be used to select an appropriate node for carrying a message towards its destination.

Ontologies could be use to ensure interoperability among VANETs applications. It also facilitates the process of sharing and using contextual information \cite{madkour2011}. Additionally, ontologies could help to represent the different categories of vehicles, how they relate with each other and with the context data. Furthermore, it assists in messages forwarding process.

Motivated by the works presented in \cite{Yokoyama_2014, ullahadvertising} that make use of beacon messages and opportunistic vehicles communications to exchange information, we propose Message Forwarding by Categorization of Vehicles (\emph{MFCV}). \emph{MFCV} is an opportunistic message forwarding protocol that make use of beacons and exploits contextual information, especially the vehicle usage category, to improve the messages delivery by consuming relatively low resources.

>>>>

Vehicular Ad hoc NETworks (VANETs) are a subclass of Mobile Ad hoc NETworks with unique characteristics like high speed of nodes and dynamic network topology. To disseminate data, VANETs enable communications between mobile nodes and infrastructure network. These networks support a large number of applications such as accident avoidance, intelligent traffic control, and data dissemination, thereby, providing safety, comfort, and convenience to the users \cite{conprova2013}.

The nodes (vehicles) in VANETs contain hundreds of onboard sensors, which provide useful information about vehicle state (e.g., engine status, vehicle position, speed, heading) and surrounding environment (e.g., road and traffic condition, and weather forecast). Vehicles that collect, disseminate and make use of this contextual information are called context-aware vehicles \cite{grilli2009}. Context-awareness is important for the deployment of a large number of new applications. However, providing reliable and efficient dissemination of contextual information is a challenging task in VANETs. It is important to share only relevant information among vehicles, in order to reduce the communication overhead \cite{kumar2015}.

The importance of vehicles categorization for providing contextual information has been recently addressed in \cite{zhang2012, zhang2014}. We can categorize the vehicles into a taxi, bus, private car, and cargo. Each of them has a different mobility pattern. For example, a bus has its own predefined route, timing, and schedule. On the other hand, a taxi has no restricted mobility and it can follow different routes at different times, based on passengers demands and drivers preferences. Such mobility information could be used to select an appropriate node for carrying a message towards its destination.

Ontologies could be used to ensure interoperability among VANETs applications. It also facilitates the process of sharing and using contextual information \cite{madkour2011}. Additionally, ontologies could help to represent the different categories of vehicles, how they relate with each other and with the context data. Furthermore, it assists in messages forwarding process.

Motivated by the works presented in \cite{Yokoyama_2014, ullahadvertising} that make use of beacon messages and opportunistic vehicles communications to exchange information, we propose Message Forwarding by Categorization of Vehicles (\emph{MFCV}). \emph{MFCV} is an opportunistic message forwarding protocol that makes use of beacons and exploits contextual information, especially the vehicle usage category, to improve the messages delivery by consuming relatively low resources.
